---
title: "Jh_eda_file"
author: "John Hanebuth"
date: "3/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in the data

```{r}
library(tidyverse)

abcfm_missionaries <-
  read_csv("abcfm_missionaries1.csv") 

abcfm_missionaries

ncol(abcfm_missionaries) 
   #1920 rows matches the number of rows in the original data.
 
 nrow(abcfm_missionaries)
#14 columns does not match the original data frame but is fine since the last columns do not have data.
  
  str(abcfm_missionaries)

abcfm_missionaries %>% 
select(mission_name) %>% 
  unique()
 
abcfm_missionaries %>% 
  select(title_in_report) %>% 
  unique()
  
#There are 20 different mission stations within the ABCFM and various stations within those stations. Five in the file are minorly altered from uniform spellings and will need to be changed.


abcfm_micronesia <-
abcfm_missionaries %>% 
  filter(mission_name == "Micronesia")

abcfm_missionaries_women <- 
  abcfm_missionaries %>% 
  filter(title_in_report == "mrs" | title_in_report == "miss")

abcfm_missionaries_women

#1065 of the 1920 total rows represent female mission workers proving that the field was rather equitable.

```

```{r}
abcfm_missionaries %>% 
  filter( MD == TRUE) %>% 
  nrow() %>% 
  print()

abcfm_missionaries_women %>% 
  filter(MD == TRUE) 
  


# There were 16 female doctors total and 87 doctors total in the ABCFM. 


# Females comprised 18.4 percent of the ABCFM medical professionals.


abcfm_missionaries_women



abcfm_missionaries_native <- 
  abcfm_missionaries %>% 
  filter(title_in_report == "native pastor")

abcfm_missionaries_native

# the number of native workers named in the annual reports represents 1/19 of the total workforce and could receive further analysis

```


```{r}
ggplot(abcfm_missionaries, aes(Report_year)) + geom_histogram()

#The histogram above only displays that the number of missionaries increased over this four year period.
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
ggplot(abcfm_micronesia, aes(x = Report_year )) + geom_bar()


ggplot(abcfm_missionaries, aes(Report_year))+geom_bar()

ggplot(abcfm_missionaries_women, aes(Report_year))+ geom_bar()

abcfm_missionaries %>% 
  group_by(Report_year) %>%
ggplot( aes(mission_name))+geom_bar() + coord_flip()
```

# The above plot shows the total number of persons associated with each mission from 1884-1887. An interesting feature of the above graphs is that the total number of missionaries associated with Turkey far exceeded the number of missionaries associated with any other geographic region.


``` {r}
ggplot(abcfm_missionaries_native, aes(Report_year))+ geom_bar()
```

#The plot above shows the number of native pastors named in ABCFM annual reports.

#Overall, the data has a few major problems. It is not tidy enough and I need to add gender as a variable. It is also tricky to plot data for each specific mission for each year, which is a problem that will need to be resolved before any further analysis can move forward. The lack of continus variables aside from year also presents a problem and it may be beneficial to include total numbers of mission congregations in a separate table to join to this one. I will also need a geographic coordinate data frame.



```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
