---
title: "Jh_eda_file"
author: "John Hanebuth"
date: "3/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in the data

```{r}
library(tidyverse)

abcfm_missionaries <-
  read_csv("abcfm_missionaries_1.csv") 

abcfm_missionaries

ncol(abcfm_missionaries) 
   #1920 rows matches the number of rows in the original data.
 
 nrow(abcfm_missionaries)
#14 columns does not match the original data frame but is fine since the last columns do not have data.
  
  str(abcfm_missionaries)

abcfm_missionaries %>% 
  arrange(mission_name) 
 
  
#There are 20 different mission stations within the ABCFM and various stations within those stations.

abcfm_micronesia <-
abcfm_missionaries %>% 
  filter(mission_name == "micronesia")

abcfm_missionaries_women <- 
  abcfm_missionaries %>% 
  filter(title_in_report == "mrs" | title_in_report == "miss")

abcfm_missionaries_women

```

```{r}
abcfm_missionaries %>% 
  filter( MD == TRUE) %>% 
  nrow() %>% 
  print()

abcfm_missionaries_women %>% 
  filter(MD == TRUE) 
  


# There were 16 female doctors total and 87 doctors total in the ABCFM. 


# Females comprised 18.4 percent of the ABCFM medical professionals.


abcfm_missionaries_women

abcfm_missionaries_native <- 
  abcfm_missionaries %>% 
  filter(title_in_report == "native pastor")

abcfm_missionaries_native

```


```{r}
ggplot(abcfm_missionaries, aes(Report_year)) + geom_histogram()

#The histogram above only displays that the number of missionaries increased over this four year period.
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
ggplot(abcfm_micronesia, aes(x = Report_year )) + geom_bar()


ggplot(abcfm_missionaries, aes(Report_year))+geom_bar()

ggplot(abcfm_missionaries_women, aes(Report_year))+ geom_bar()

abcfm_missionaries %>% 
  group_by(Report_year) %>%
ggplot( aes(mission_name))+geom_bar() + coord_flip()
```

# The above plot shows the total number of persons associated with each mission from 1884-1887. An interesting feature of the above graphs is that the total number of missionaries associated with Turkey far exceeded the number of missionaries associated with any other geographic region.


``` {r}
ggplot(abcfm_missionaries_native, aes(Report_year))+ geom_bar()
```

#The plot above shows the number of native pastors named in ABCFM annual reports.

#Overall, the data has a few major problems. It is not tidy enough and I need to add gender as a variable. It is also tricky to plot data for each specific mission for each year, which is a problem that will need to be resolved before any further analysis can move forward.



# This plot shows that my data is not very tidy.
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
